The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
it's bibliography: not references:

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
header-includes: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland

output: 
    bookdown::word_document2:
      reference_docx: template.docx
    # github_document

references: ../references/knitcite.bib
---

>>>>

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
header-includes: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output: 
    # bookdown::word_document2:
      # reference_docx: template.docx
    github_document
bibliography: ../references/knitcite.bib
---
